SDR enhancement by clouds \\\large{A Short Subtitle}

### 2023-11-28 article/article.qmd
Commit 2023-11-28 12:14

Clear sky identification
- helps on determining thresholds

Criteria for enhancement based on TSI
- some other were tested

>>>>

### Data selection

To preserve an unbiased representation of the data we applied a constrain similar the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset. Days with less than 5 valid hours are rejected completely.

<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid. There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid. -->

-   CastillejoCuberos2020
-   valid data 45min /h and 5h / day
-   SZA above biology

Clear sky identification

-   helps on determining thresholds

Criteria for enhancement based on TSI

-   some other were tested

### 2023-11-28 article/article.tex
Commit 2023-11-28 12:14

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

@@

@@

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, opacitybacktitle=0.6, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, opacityback=0, bottomrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, coltitle=black, colback=white]

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

@@

\hypertarget{data-selection}{%
\subsubsection{Data selection}\label{data-selection}}

To preserve an unbiased representation of the data we applied a
constrain similar the one used by \citet{CastillejoCuberos2020}. Where,
for each valid hour of day, there must exist at list 45 minutes of valid
measurements, including night time, near dusk and dawn. Days with less
than 5 complete hours are rejected completely.

\begin{itemize}
\tightlist
\item
  CastillejoCuberos2020
\item
  valid data 45min /h and 5h / day
\item
  SZA above biology
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  helps on determining thresholds
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  some other were tested
\end{itemize}

@@

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, left=2mm, rightrule=.15mm, bottomrule=.15mm, colframe=quarto-callout-important-color-frame, colback=white, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, bottomtitle=1mm, toptitle=1mm, coltitle=black, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, titlerule=0mm, arc=.35mm, opacityback=0, leftrule=.75mm]
